%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Doctor of Philosophy \newline Master of Philosophy \newline Master of Arts} % Degree
    {\href{http://polisci.columbia.edu/}{Political Science Department}, \href{http://www.columbia.edu/}{Columbia University}} % Institution
    {New York, NY, US} % Location
    {Sep. 2014 - PRESENT \newline Sep. 2014 - PRESENT \newline Sep. 2014 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Major: \emph{Comparative Politics}}
        \item {Minor: \emph{Political Economy}}
      \end{cvitems}
    }

\cventry
    {Candidate of Sciences (PhD Equivalent)} % Degree
    {\href{http://isc.hse.ru/about_eng}{LAAISC (CInSt)}, \href{http://www.hse.ru/en/}{NRU Higher School of Economics}} % Institution
    {Moscow, Russia} % Location
    {Nov. 2011 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis Topic: \emph{Taming the (not so) Stationary Bandit: Property Rights and Political Competition in Non-democratic Setting}}
        \item {Candidacy Program: \emph{Theoretical Economics}}
        \item {Advisor: \href{http://www.hse.ru/en/org/persons/65104}{Professor Leonid I.~Polishchuk}}
      \end{cvitems}
    }

\cventry
    {Master of Economics \newline Bachelor of Economics} % Degree
    {\href{http://economics.hse.ru/en/}{Department of Economics}, \href{http://www.hse.ru/en/}{NRU Higher School of Economics}} % Institution
    {Moscow, Russia} % Location
    {Sep. 2009 - Jul. 2011 \newline Sep. 2005 - Jul. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Master Thesis Topic: \emph{Property Rights and Political Competition: Economic Analysis}}
        \item {Area of Study: \emph{Political Economy}, \emph{Endogenous Property Rights}, \emph{Institutional Economics}}
        \item {Advisor: \href{http://www.hse.ru/en/org/persons/65104}{Professor Leonid I.~Polishchuk}}
      \end{cvitems}
    }

% \cventry
%     {Bachelor of Economics} % Degree
%     {\href{http://economics.hse.ru/en/}{Department of Economics}, \href{http://www.hse.ru/en/}{NRU Higher School of Economics}} % Institution
%     {Moscow, Russia} % Location
%     {Sep. 2005 - Jul. 2009} % Date(s)
%     {
%       \begin{cvitems} % Description(s) bullet points
%         \item {Concentration: \emph{Risk-management} (with emphasis on stochastic methods of actuarial analysis)}
%       \end{cvitems}
%     }
%---------------------------------------------------------
\end{cventries}
